### 2023-01-10 draft/draft.Rmd
responded to more comments

\begin{example}[Assortativity and disassortativity of the two-community SBM]
\label{ex:sbm-assortativity}
Let $P$ be the $n \times n$ probability matrix of a two-community SBM. 
Then $rank(P) = 2$, and its two nonzero eigenvalues are:

\begin{equation}
\label{eq:sbm-eigenvalues}
\lambda = \frac{n}{2} \bigg( 
\theta_{11} + \theta_{22} \pm 
\sqrt{(\theta_{11} - \theta_{22})^2 + 4 \theta_{12}^2} 
\bigg).
\end{equation}
The first eigenvalue is always positive. 
The second eigenvalue is positive if $\theta_{11} \theta_{22} > \theta_{12}^2$. 
Thus, $P$ describes an assortative SBM if $\theta_{11} \theta_{22} > \theta_{12}^2$ or 
a disassortative SBM if $\theta_{11} \theta_{22} < \theta_{12}^2$. 
This corresponds to the high-level understanding of assortativity and disassortativity based on whether within community edge probabilities are greater than the between community edge probabilities. 
\end{example}

>>>>

\begin{example}[Assortativity and disassortativity of the two-community SBM]
\label{ex:sbm-assortativity}
Let $P$ be the $n \times n$ probability matrix of a two-community SBM. 
Then $P$ can be written as $P = Z \Theta Z^\top$ where $\Theta$ is the $2 \times 2$ matrix of the community edge probabilities $\{\theta_{k \ell}\}$, and $Z$ is an $n \times 2$ matrix such that $z_{ik} = 1$ if vertex $i$ is in community $k$ and $0$ otherwise. 
The rank of $\Theta$ is 2, and  its two nonzero eigenvalues are:
\begin{equation}
\label{eq:sbm-eigenvalues}
\lambda = \bigg( 
\theta_{11} + \theta_{22} \pm 
\sqrt{(\theta_{11} - \theta_{22})^2 + 4 \theta_{12}^2} 
\bigg).
\end{equation}
The first eigenvalue is always positive. 
The second eigenvalue is positive if $\theta_{11} \theta_{22} > \theta_{12}^2$. 
Since the rank and positive semidefiniteness of $P$ is given by $\Theta$, $P$ is positive semidefiniteif $\theta_{11} \theta_{22} > \theta_{12}^2$, which correspond to assortative and disassortative SBMs. 
This corresponds to the high-level understanding of assortativity and disassortativity based on whether within community edge probabilities are greater than the between community edge probabilities. 
\end{example}

### 2023-01-10 draft/draft.tex
responded to more comments

%\begin{titlepage}
\begin{center}
\LARGE{\textsc{Community Detection in the Setting of Generalized Random Dot Product Graphs}}\\
\vspace*{4\baselineskip}
\normalsize{John Koo}\\
\vspace*{8\baselineskip}
\singlespacing
\normalsize{Submitted to the faculty of the Univesity Graduate School \\
in partial fulfillment of the requirements for the degree \\
Doctor of Philosophy \\
in the Department of Statistics, \\
Indiana University \\
December 2022}
\vspace*{3\baselineskip}

>>>>

%\begin{titlepage}
\begin{center}
\LARGE{\textsc{Community Detection in the Setting of Generalized Random Dot Product Graphs}}\\
\vspace*{4\baselineskip}
\normalsize{John Koo}\\
\vspace*{8\baselineskip}
\singlespacing
\normalsize{Submitted to the faculty of the Univesity Graduate School \\
in partial fulfillment of the requirements for the degree \\
Doctor of Philosophy \\
in the Department of Statistics, \\
Indiana University \\
January 2023}
\vspace*{3\baselineskip}
